\documentclass[11pt,a4paper]{article}

\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{setspace}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=black
}

\setstretch{1.15}
\setlist[itemize]{leftmargin=1.5em}
\titleformat{\section}{\large\bfseries}{}{0em}{}

\begin{document}

\begin{center}
    {\LARGE \textbf{Professional Contribution Report}}\\[6pt]
    {\large Quiz Application Project}\\[10pt]
    \textbf{Date:} March 31, 2026
\end{center}

\vspace{0.8cm}

\section*{Executive Summary}
This report documents professional contributions across the full delivery lifecycle of the Quiz Application project, with direct ownership in frontend engineering, backend engineering, and DevOps/deployment operations. The work focused on production readiness, reliability, maintainability, and smooth end-user experience.

\section*{Role Scope}
\begin{itemize}
    \item \textbf{Frontend Engineering:} User interface implementation, page/component integration, and client-side experience improvements.
    \item \textbf{Backend Engineering:} API stability, middleware/configuration updates, service hardening, and operational troubleshooting.
    \item \textbf{DevOps \& Deployment:} Environment/deployment configuration, release support, production validation, and post-deployment reliability improvements.
\end{itemize}

\section*{Key Contributions}

\subsection*{1) Frontend Contributions}
\begin{itemize}
    \item Supported and maintained React-based application views and interaction flows.
    \item Improved frontend-backend integration behavior for production scenarios.
    \item Contributed to overall UX consistency and operational reliability from the client side.
\end{itemize}

\subsection*{2) Backend Contributions}
\begin{itemize}
    \item Strengthened FastAPI service behavior for stable production usage.
    \item Removed dependency paths that introduced avoidable runtime risk (notification-related coupling).
    \item Updated middleware/network handling to reduce cross-origin request failures.
    \item Performed endpoint-level validation and iterative fixes to ensure service continuity.
\end{itemize}

\subsection*{3) DevOps and Deployment Contributions}
\begin{itemize}
    \item Participated in deployment configuration and production environment alignment.
    \item Reviewed and cleaned configuration artifacts to remove unnecessary bindings.
    \item Executed production-focused troubleshooting and verification after release.
    \item Ensured dependable communication between deployed frontend and backend services.
\end{itemize}

\section*{Operational Impact}
\begin{itemize}
    \item Improved production stability by reducing non-essential service dependencies.
    \item Reduced integration issues through corrected cross-origin configuration.
    \item Increased deployment reliability via configuration cleanup and validation.
    \item Strengthened confidence in live operations through endpoint testing and monitoring.
\end{itemize}

\section*{Conclusion}
The contribution profile demonstrates end-to-end ownership across frontend, backend, and DevOps/deployment domains. The delivered work materially improved deployment quality, runtime stability, and production integration outcomes for the Quiz Application project.

\vspace{0.6cm}
\noindent\textbf{Prepared by:} Project Contributor\\
\textbf{Project:} Quiz Application\\
\textbf{Report Date:} March 31, 2026

\end{document}
